---
title: "Considering Degree Centrality for More Descriptive Communities in Social Network Analysis"
format: 
  revealjs:
    incremental: false
    slide-number: true
    logo: https://canpath.ca/wp-content/uploads/2020/03/dalla-lana-logo@2x.png
    footer: "Smith, Benjamin (2024): Considering Degree Centrality for More Descriptive Communities in Social Network Analysis"
    html-math-method: katex
    
css: style.css
editor: source
author: 
  name: Benjamin Smith
  degree: Dalla Lana School of Public Health
  orcid: 0009-0007-2206-0177
  email: benyamin.smith@mail.utoronto.ca

---

## Social Networks

```{r}
library(igraph)
library(igraphdata)
library(ig.degree.betweeness)

data("karate")
data("UKfaculty")

uk_faculty <- ig.degree.betweeness::prep_unlabeled_graph(UKfaculty)

sim <- igraph::sample_smallworld(1, 100, 5, 0.1)|>
  ig.degree.betweeness::prep_unlabeled_graph()


par(mfrow = c(1,3), mar=c(0,0,0,0)+.1)

plot(karate,
     edge.arrow.size = 0.3)

plot(uk_faculty,
     vertex.color = V(UKfaculty)$Group,
     edge.arrow.size = 0.3)

plot(sim)
```

## Social Network Analysis


-   __Social network analysis (SNA)__: a process used for analysis of social structure by the use of networks and graph-theory.


::: {.fragment fragment-index=1}
-  Social networks are made up of two building blocks:
:::

<!--
Get pictures of nodes and edges
--->

::: {.fragment fragment-index=2}
:::: {.columns}

::: {.column width="50%"}

__Nodes__

```{r}
g <- graph(c(1, 2, 2, 3, 3, 1), directed = TRUE)
par(mar=c(0,0,0,0)+.1)
V(g)$color <- "red"

plot(g,
     vertex.label = "",
     edge.arrow.size = 1,
     vertex.size = 20)
```


:::

::: {.column width="50%"}

__Edges__

```{r}
V(g)$color <- "grey"
E(g)$color <- "red"
par(mar=c(0,0,0,0)+.1)

plot(g,
     vertex.label = "",
     edge.arrow.size = 1,
     vertex.size = 20)
```

:::
:::: 
:::


## Community Detection

## Modularity


- A popular metric which is optimized in community detection algorithms is __modularity__.



::: {.fragment fragment-index=3}
- function calculates the strength of the division of a graph into subgraphs.
:::


::: {.fragment fragment-index=4}
:::: {.columns}

::: {.column width="50%"}

__Undirected__

- Clauset et al (2004): 

$$
\begin{aligned}
Q=\frac{1}{2m} \sum_{i,j}(A_{ij}-\gamma\frac{k_i k_j}{2m})\delta(c_i,c_j)
\end{aligned}
$$
:::

::: {.column width="50%"}

__Directed__

- `igraph` R package (2024):

$$
Q = \frac{1}{m} \sum_{i,j} (A_{ij}-\gamma\frac{k_i^\text{out} k_j^\text{in}}{m})\delta(c_i,c_j)
$$
:::
:::: 
:::

:::{.incremental}
- $m=$ no. of edges; $A_{ij}=$ the $(i,j)^{th}$ element in the adjacency matrix
- $k_i$ and $k_j$: the degree (no. of connections) in nodes $i$ and $j$
- $\delta(c_i, c_j)$ indicator function of existence of a path between two nodes. 
- $\gamma=$ resolution paramter (default $\gamma= 1$)
:::


## Edge Betweeness (Girvan-Newman)

## Louvain

## Degree Betweeness (Smith-Pittman)

# Results

## Zachary's Karate Club Network

## Friendship network of UK university faculty

## Watts-Strogatz small-world model

# Discussion

## Discussion

## Limitations and Further Work

## Acknowledgements

## References

::: {style="font-size:15px"}
::: nonincremental
1. M. Rostami, M. Oussalah, K. Berahmand & V. Farrahi, "Community Detection Algorithms in Healthcare Applications: A Systematic Review," in IEEE Access,11, pp. 30247-30272, 2023, doi: 10.1109/ACCESS.2023.3260652.

2. A. Clauset, M. E. J. Newman, & C. Moore, (2004). Finding community structure in very large networks. Phys. Rev. E, 70(6), 066111. doi: 10.1103/PhysRevE.70.066111

3. G. Csárdi,T. Nepusz, V. Traag, Sz. Horvát, F. Zanini & D. Noom,K. Müller (2024). igraph: Network Analysis and Visualization in R. doi:10.5281/zenodo.7682609, R package version 1.5.1,https://CRAN.R-project.org/package=igraph.

4.  M. Girvan, & M. E. J. Newman (2002). Community structure in social and biological networks. Proceedings of the National Academy of Sciences of the United States of America, 99(12), 7821–7826. https://doi.org/10.1073/pnas.122653799

5. M. E. J. Newman, & M. Girvan, (2004). Finding and evaluating community structure in networks. Phys. Rev. E, 69(2), 026113. doi: 10.1103/PhysRevE.69.026113

6. V. D. Blondel, J. Guillaume, R. Lambiotte, & E. Lefebvre, (2008). Fast unfolding of communities in large networks. Journal of Statistical Mechanics: Theory and Experiment, 2008(10), P10008. https://doi.org/10.1088/1742-5468/2008/10/p10008

7. N. Smith, P. N. Zivich, L. Frerichs, J. Moody, & A. E. Aiello, (2020). A guide for choosing community detection Algorithms in social network Studies: The question Alignment Approach. American Journal of Preventive Medicine, 59(4), 597–605. https://doi.org/10.1016/j.amepre.2020.04.015

8. W. Zachary, (1977). An information flow model for conflict and fission in small groups. Journal of Anthropological Research, 33(4), 452–473. https://doi.org/10.1086/jar.33.4.3629752

9. T. Nepusz, A. Petróczi, L. Négyessy, & F. Bazsó, (2008). Fuzzy communities and the concept of bridgeness in complex networks. Physical Review E, 77(1). https://doi.org/10.1103/physreve.77.016107

10.  D. J. Watts, & S. H. Strogatz, (1998). Collective dynamics of ‘small-world’ networks. Nature, 393(6684), 440–442. https://doi.org/10.1038/30918

11. G Csardi, (2015). igraphdata: A Collection of Network Data Sets for the 'igraph' Package. R
  package version 1.0.1, https://CRAN.R-project.org/package=igraphdata.

12. M. A. Porter, (2012). Small-world network. Scholarpedia, 7(2), 1739. https://doi.org/10.4249/scholarpedia.1739

13. A. P. Christensen, (2023). Comparing community detection Algorithms in psychometric networks: A Monte Carlo simulation. OSF. https://doi.org/10.17605/OSF.IO/JFXAD
::: 
:::

# Thank You!


